General writeup

### 2017-11-27 Latex/general_writeup.tex
In latex file 1.4 and 1.6 are two great specifications in line amopng them!

	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_01_19}

	\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_09}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_14}}
\end{figure}

>>>>

	\input{FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}

	\begin{figure}[h!]
\centering
\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_27-Nov-2017_12_27_25}} \hspace{.2in%
} 
\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_27-Nov-2017_12_27_30}}
\end{figure}
